Towards Patient-Specific Neural Field Modeling using Micro-Electrode Data

### 2011-05-12 ltx/data_paper/DataPaper.tex
added computational complexity

Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly. In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases.

\section{Results}
This section demonstrates the identification of the proposed IDE model using simulated data. The observation noise and disturbance were unknown and no assumption were made on the shape of the kernel.  Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state. The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ . The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations. The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$. The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively. The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.

>>>>

Given the state estimates, $\mathbf {\hat x}_t$ the state covariance $\mathbf P_t$ and cross-covariance $\mathbf M_t$ , the $\boldsymbol\Xi$-variables can be computed directly. In the M-step, an update $\boldsymbol\Theta'$ is chosen such that $\mathcal{Q}\left(\boldsymbol\Theta',\boldsymbol\Theta'\right)>\mathcal{Q}\left(\boldsymbol\Theta,\boldsymbol\Theta'\right)$, this will guarantee that the likelihood increases. The computational complexity of the algorithm is given ib Table
 \begin {table}
\begin{center}
\scalebox{1}{\begin{tabular}{lll}
\hline \hline
Variable &Order&Order of the approximate\\ \hline\\
$\Xi_0, \Xi_1, \Xi_2$&$O(Tn_x^2)$&-\\
$\Xi_3, \Xi_5$&$O(Tn_x^3)+O(Tn_x^2n_{\theta})$&$O(Tn_x^3n_r^2)+O(Tn_x^2n_{\theta}n_r^2)$ \\
$\Xi_4$&$O(Tn_x^3n_{\theta})+O(Tn_x^2n_{\theta}^2)$&$O(Tn_x^3n_{\theta}n_r^2)+O(Tn_x^2n_{\theta}^2n_r^2)$\\
$\hat{\boldsymbol\theta} $&$O(n_{\theta}^3)$&-\\
$\hat{\xi}$&$O(n_x^3+n_{\theta}^3)$&-\\
 $\hat{\sigma}_{\epsilon}^2$&$O(Tn_y^2n_x^2)$&-\\
$\hat{\sigma}_{d}^2$&$O(Tn_x^3)+O(Tn_{\theta}^3)&-$\\
\hline \hline
\end{tabular}}
 \caption {Computational complexity of EM algorithm} 
\label{table:BsplineConvolutionandInnerproduct}
\end{center}
\end {table}

\section{Results}
This section demonstrates the identification of the proposed IDE model using simulated data. The observation noise and disturbance were unknown to the estimation algorithm and no assumption were made on the shape of the kernel.  Data was generated employing state space equation (\ref{eq:StateEq}-\ref{eq:QmatrixForSigmapoints}) using a square grid of $n_x= 9 \times 9$ equally spaced ($2.5~mm$) basis functions with $\sigma_{\phi}^2=1.58~mm^2$, assuming the observed field can be fully described by the decomposed IDE model. 100 realizations of 500 ms of data were generated and the first 100 ms was discarded allowing the model's dynamic to reach steady state. The observation noise was set to $\Sigma_{\epsilon}=0.2\times \mathbf I_{n_y}$ and the field disturbance was set to $\mathcal{GP}(\mathbf 0,0.1 \times\gamma(\mathbf{r}-\mathbf{r}'))$ where the covariance function was chosen as a Gaussian with zero mean and the width $\sigma_{\gamma}^2=1.7~mm^2$ . The distance between adjacent sensors was 1.5 mm resulting into $n_y = 196$ observations. The width of the sensor kernels were set to $\sigma_m^2=0.81~mm^2$. The sampling period and the synaptic time constant were set to $T_s = 1~ms$  and $\tau = 10~ms$, respectively. The sigmoidal activation parameters were $\varsigma=0.56~mV^{-1}$ and $v_0=1.8~mV$.
